Analysis after review

### 2020-05-26 reports/DRM_exp/analysis_DRM_after_review.Rmd
add ground-truth memorability score

## FAbility - with category corrections

```{r}
df

>>>>

## How many scenes have ground-truth memorability score

df_memorability_ground_truth <- read_csv(here("data/exp_DRM1/memorability/figrim_memorability_within_category.csv"))
dfm <- dfm %>% left_join(df_memorability_ground_truth, by = c("img_name"="filename"))
dfm1 <- dfm %>% 
  group_by(type,img_name) %>% 
  mutate( HR = hits/(hits+misses),
          FR = false_alarms/(false_alarms+correct_rejections)) %>% 
  summarize(hits = mean(hits), fa = mean(false_alarms),HR = mean(HR), FR = mean(FR), correct = mean(correct),mem_score = mean(mem_score)) %>% 
  ungroup() 
dfm1 %>% 
  group_by(type) %>% 
  summarize(n_perc = sum(!is.na(hits))/n(), n=sum(!is.na(hits)))
dfm1 %>% 
  group_by(type) %>% 
  do(cor.test(~HR+correct,.) %>% broom::tidy())
dfm1 %>% 
  group_by(type) %>% 
  mutate(correct = 1-correct) %>% 
  do(cor.test(~FR+correct,.) %>% broom::tidy())

dfm1 %>% 
  group_by(type) %>% 
  do(cor.test(~mem_score+FR,.) %>% broom::tidy())
